---
title: "lies"
output: html_document
---

# setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(stats4)
library(scales)
library(cowplot)
source("lying_modelFunctions.R")
bs.final <- read.csv("bsfinal_anon.csv")
humanLie <- bs.final %>%
  filter(roleCurrent == "bullshitter")

#counts of human reports in matrix
template <- data.frame(expt=rep("expt0",11),
                       probabilityRed = rep(0,11),
                       drawnRed = rep(0,11),
                       reportedDrawn = 0:10,
                       n = rep(0,11))
countsLie <- humanLie %>%
  group_by(expt, probabilityRed, drawnRed, reportedDrawn) %>%
  count()
countsLie <- bind_rows(template,countsLie) %>%
  complete(expt, probabilityRed, drawnRed, reportedDrawn, fill=list(n=0)) %>%
  filter(expt != "expt0", probabilityRed != 0)



humanDetect <- bs.final %>%
  filter(roleCurrent == "bullshitDetector")

template2 <- data.frame(expt=rep("expt0",2),
                       probabilityRed = rep(0,2),
                       reportedDrawn = rep(0,2),
                       callBS = c("False", "True"),
                       n = rep(0,2))
countsDetect <- humanDetect %>%
  group_by(expt, probabilityRed, reportedDrawn, callBS) %>%
  count()
countsDetect <- bind_rows(template2,countsDetect) %>%
  complete(expt, probabilityRed, reportedDrawn, fill=list(n=0)) %>%
  filter(expt != "expt0", probabilityRed != 0)

logitToProb <- function(logit){
  exp(logit) / (1+exp(logit))
}

probToLogit <- function(prob){
  log(prob / (1 - prob))
}
```

# Models of lying

## sender / liar

these are all models that consider payoffs but not baserates.

### everyone lies by some small amount

$$P(k^* \mid k) = \phi((k^* - k)*SIGN(U) \mid \theta)$$

$$\phi=?$$  
geometric? 
poisson?  (probably poisson is best)

```{r}
allLies.poisson <- function(k, kstar, util, theta, weight){
  weight = logitToProb(pmin(10, pmax(-10, weight)))
  theta = exp(theta)
  log(weight*dpois((kstar-k)*util, theta)/ppois(ifelse(util==1, 10-k, k), theta)+(1-weight)*(1/11))
}

allLies.LL <- function(theta, weight){
  k = humanLie$drawnRed
  kstar = humanLie$reportedDrawn
  expt = humanLie$expt
  util = ifelse(expt=="expt4", 1, -1)
  
  pred = allLies.poisson(k, kstar, util, theta, weight)
  # likelihood of observed kstar for that k, given parameters
  neg.log.lik = -1*sum(pred)
  neg.log.lik
}

allLies.fit <- summary(mle(allLies.LL,
           start=list(theta=rnorm(1, 0, 1),
                      weight=rnorm(1, 0, 1)),
           method = "BFGS"))
allLies.fit

humanLie.predAllLies <- data.frame(k=rep(rep(0:10, each=11),2), 
                                    kstar=rep(0:10, 11*2),
                                    util=rep(c(1,-1),each=11*11)) %>%
  mutate(predicted = exp(allLies.poisson(k, kstar, util, allLies.fit@coef['theta','Estimate'], allLies.fit@coef['weight','Estimate'])))

humanLie.predAllLies %>%
  group_by(util,k) %>%
  summarise(sum=sum(predicted))

humanLie.predAllLies %>%
  mutate(util = ifelse(util == 1, "sender gets points for red", "sender gets points for blue"),
         util = fct_relevel(util,"sender gets points for red", "sender gets points for blue")) %>%
  ggplot(aes(x=k, y=kstar, fill=predicted)) +
  geom_tile() +
  scale_x_continuous("true drawn k", breaks=seq(0,10,2), expand=c(0,0)) +
  scale_y_continuous("reported k*", breaks=seq(0,10,2), expand=c(0,0)) +
  scale_fill_gradient(low="white",high="navy") +
  facet_wrap(~util) +
  theme_bw()
ggsave("img/simpleModels/allLies.png", width=7, height=3.45)




allLies.pred.full <- humanLie.predAllLies %>%
  mutate(util = ifelse(util == 1, "sender gets points for red", "sender gets points for blue"),
         util = fct_relevel(util,"sender gets points for red", "sender gets points for blue")) %>%
  slice(rep(1:n(), 3)) %>%
  mutate(p = rep(c(0.2, 0.5, 0.8), each=242),
         p = as.factor(paste("p =",p)))

allLies.pred.red.fig <- allLies.pred.full %>%
  filter(util == "sender gets points for red") %>%
  ggplot(aes(x=k, y=kstar, fill=predicted)) +
  geom_tile() +
  scale_x_continuous("", breaks=seq(0,10,2), expand=c(0,0)) +
  scale_y_continuous("\n\nEverybody Lies", breaks=seq(0,10,2), expand=c(0,0)) +
  scale_fill_gradient(low="white",high="navy", limits=c(0,1)) +
  guides(fill=FALSE) +
  facet_wrap(~p) +
  theme_bw()

allLies.pred.blue.fig <- allLies.pred.full %>%
  filter(util == "sender gets points for blue") %>%
  ggplot(aes(x=k, y=kstar, fill=predicted)) +
  geom_tile() +
  scale_x_continuous("", breaks=seq(0,10,2), expand=c(0,0)) +
  scale_y_continuous("\n\nEverybody Lies", breaks=seq(0,10,2), expand=c(0,0)) +
  scale_fill_gradient(low="white",high="navy", limits=c(0,1)) +
  guides(fill=FALSE) +
  facet_wrap(~p) +
  theme_bw()
```

### some fraction of people lie by some amount

$$P(k^* \mid k) = \begin{cases}
k=k^* & p\\
k\neq k^* & (1-p) \cdot phi(k^* - k \mid \theta, SIGN(u))
\end{cases}$$

```{r}
someLies.poisson <- function(k, kstar, p, util, theta, weight){
  p = logitToProb(pmin(10, pmax(-10, p)))
  weight = logitToProb(pmin(10, pmax(-10, weight)))
  theta = exp(theta)
  log((k==kstar)*p + (1-p)*(weight*dpois((kstar-k)*util, theta)/ppois(ifelse(util==1, 10-k, k), theta) + (1-weight)/11))
}

someLies.LL <- function(p, theta, weight){
  k = humanLie$drawnRed
  kstar = humanLie$reportedDrawn
  expt = humanLie$expt
  util = ifelse(expt=="expt4", 1, -1)
  
  pred = someLies.poisson(k, kstar, p, util, theta, weight)
  # likelihood of observed kstar for that k, given parameters
  neg.log.lik = -1*sum(pred)
  neg.log.lik
}

someLies.fit <- summary(mle(someLies.LL,
           start=list(p=rnorm(1,0,1),
                      theta=rnorm(1, 0, 1),
                      weight=rnorm(1, 0, 1)),
           method = "BFGS"))
someLies.fit

humanLie.predSomeLies <- data.frame(k=rep(rep(0:10, each=11),2), 
                                    kstar=rep(0:10, 11*2),
                                    util=rep(c(1,-1),each=11*11)) %>%
  mutate(predicted = exp(someLies.poisson(k, kstar, someLies.fit@coef['p','Estimate'], util, someLies.fit@coef['theta','Estimate'], someLies.fit@coef['weight','Estimate'])))

humanLie.predSomeLies %>%
  mutate(util = ifelse(util == 1, "sender gets points for red", "sender gets points for blue"),
         util = fct_relevel(util,"sender gets points for red", "sender gets points for blue")) %>%
  ggplot(aes(x=k, y=kstar, fill=predicted)) +
  geom_tile() +
  scale_x_continuous("true drawn k", breaks=seq(0,10,2), expand=c(0,0)) +
  scale_y_continuous("reported k*", breaks=seq(0,10,2), expand=c(0,0)) +
  scale_fill_gradient(low="white",high="navy") +
  facet_wrap(~util) +
  theme_bw()
ggsave("img/simpleModels/someLies.png", width=7, height=3.45)




someLies.pred.full <- humanLie.predSomeLies %>%
  mutate(util = ifelse(util == 1, "sender gets points for red", "sender gets points for blue"),
         util = fct_relevel(util,"sender gets points for red", "sender gets points for blue")) %>%
  slice(rep(1:n(), 3)) %>%
  mutate(p = rep(c(0.2, 0.5, 0.8), each=242),
         p = as.factor(paste("p =",p)))

someLies.pred.red.fig <- someLies.pred.full %>%
  filter(util == "sender gets points for red") %>%
  ggplot(aes(x=k, y=kstar, fill=predicted)) +
  geom_tile() +
  scale_x_continuous("", breaks=seq(0,10,2), expand=c(0,0)) +
  scale_y_continuous("\n\nSome People Lie", breaks=seq(0,10,2), expand=c(0,0)) +
  scale_fill_gradient(low="white",high="navy", limits=c(0,1)) +
  guides(fill=FALSE) +
  facet_wrap(~p) +
  theme_bw()

someLies.pred.blue.fig <- someLies.pred.full %>%
  filter(util == "sender gets points for blue") %>%
  ggplot(aes(x=k, y=kstar, fill=predicted)) +
  geom_tile() +
  scale_x_continuous("", breaks=seq(0,10,2), expand=c(0,0)) +
  scale_y_continuous("\n\nSome People Lie", breaks=seq(0,10,2), expand=c(0,0)) +
  scale_fill_gradient(low="white",high="navy", limits=c(0,1)) +
  guides(fill=FALSE) +
  facet_wrap(~p) +
  theme_bw()
```

### random opponent

sender based on baseline detector?
are there any parameters here to optimize?

```{r}
# noToM_liar <- data.frame(role=factor(),
#                       p=numeric(), 
#                       expt=factor(),
#                       mor=numeric(),
#                       k=numeric(),
#                       ksay=numeric(),
#                       val=numeric(),
#                       n=numeric())
# 
# for(m in -5:25){
#   moral = m
#   for(i in c(0.2, 0.5, 0.8)){
#     for(j in c(4,5)){
#       Expt = j
#       sim.D <- p.L_ksay.k.r(i, TRUE, iterate.D(0,i,rep(0.5,11)))
#       
#       noToM_liar <- bind_rows(noToM_liar,
#                               data.frame(role="Liar", p=i, expt=paste0("expt",j),
#                                          mor=m,
#                                          k = rep(0:10, each=11),
#                                          ksay = rep(0:10, 11),
#                                          val=as.vector(sim.D),
#                                          n=1))
#     }
#   }
# }
# 
# write_csv(noToM_liar, "lie-models/noToM_sender_all.csv")
noToM_liar <- read_csv("lie-models/noToM_sender_all.csv")

full.counts <- countsLie %>%
  group_by(expt, drawnRed, reportedDrawn) %>%
  summarise(n = sum(n))

logliks_randomOpp_m.l <- data.frame(mor = numeric(), loglik = numeric())
for(m in unique(noToM_liar$mor)){
  tempProd <- 0
  noToM_liar.mX <- filter(noToM_liar, mor==m)
  for(e in c("expt4","expt5")){
    for(t in 0:10){
      this.matr <- matrix(filter(noToM_liar.mX,expt==e, p==0.5)$val, nrow=11, ncol=11) #matrix for p=0.2, 0.5, 0.8 are the same
      this.counts <- filter(full.counts, expt==e, drawnRed==t)
      n <- this.counts$n
      total <- sum(this.counts$n)
      loglik <- sum(log(this.matr[,(t+1)])*n) #equiv to log of product
      #loglik <- dmultinom(n, total, this.matr[,(t+1)], log=T)
      #print(paste(e, ",", "true =", t, ":", loglik))
      tempProd <- tempProd + loglik
    }
  }
  logliks_randomOpp_m.l <- bind_rows(logliks_randomOpp_m.l, data.frame(mor=m, loglik=tempProd))
}

best.randOpp <- logliks_randomOpp_m.l %>%
  filter(loglik == max(loglik))

noToM_liar %>%
  filter(mor == best.randOpp$mor) %>%
  mutate(expt = ifelse(expt == "expt4", "sender gets points for red", "sender gets points for blue"),
         expt = fct_relevel(expt,"sender gets points for red", "sender gets points for blue")) %>%
  ggplot(aes(x=k, y=ksay, fill=val)) +
  geom_tile(stat="identity") +
  ggtitle(paste0("Random Opponent + Aversion (η=",best.randOpp$mor,")")) +
  scale_x_continuous("true drawn k", breaks=seq(0,10,2), expand=c(0,0)) +
  scale_y_continuous("reported k*", breaks=seq(0,10,2), expand=c(0,0)) +
  scale_fill_gradient("predicted", low="white",high="navy") +
  facet_grid(expt ~ p)
ggsave("img/simpleModels/noToM_sender.png", width=7, height=4.6)




noToM_liar.pred.full <- noToM_liar %>%
  filter(mor == best.randOpp$mor) %>%
  mutate(expt = ifelse(expt == "expt4", "sender gets points for red", "sender gets points for blue"),
         expt = fct_relevel(expt,"sender gets points for red", "sender gets points for blue"),
         p = as.factor(paste("p =",p)))

noToM_liar.pred.red.fig <- noToM_liar.pred.full %>%
  filter(expt == "sender gets points for red") %>%
  ggplot(aes(x=k, y=ksay, fill=val)) +
  geom_tile() +
  scale_x_continuous("", breaks=seq(0,10,2), expand=c(0,0)) +
  scale_y_continuous("reported k*\n\nNo ToM", breaks=seq(0,10,2), expand=c(0,0)) +
  scale_fill_gradient(low="white",high="navy", limits=c(0,1)) +
  guides(fill=FALSE) +
  facet_wrap(~p) +
  theme_bw()

noToM_liar.pred.blue.fig <- noToM_liar.pred.full %>%
  filter(expt == "sender gets points for blue") %>%
  ggplot(aes(x=k, y=ksay, fill=val)) +
  geom_tile() +
  scale_x_continuous("", breaks=seq(0,10,2), expand=c(0,0)) +
  scale_y_continuous("reported k*\n\nNo ToM", breaks=seq(0,10,2), expand=c(0,0)) +
  scale_fill_gradient(low="white",high="navy", limits=c(0,1)) +
  guides(fill=FALSE) +
  facet_wrap(~p) +
  theme_bw()
```

### iterated recursive liar behavior

```{r}
# iteratedToM_liar <- data.frame(role=factor(),
#                       p=numeric(),
#                       expt=factor(),
#                       mor=numeric(),
#                       depth=numeric(),
#                       k=numeric(),
#                       ksay=numeric(),
#                       val=numeric())
# 
# for(i in c(0.2, 0.5, 0.8)){
#   for(j in -5:25){
#     moral = j
#     for(k in c(4,5)){
#       Expt = k
#       for(d in 0:40){
#         sim.L <- p.L_ksay.k.r(i, lastlvl=TRUE, iterate.D(d, i, rep(0.5,11)))
# 
#         iteratedToM_liar <- bind_rows(iteratedToM_liar,
#                                 data.frame(role="Liar", p=i, expt=paste0("expt",k),
#                                       mor=j,
#                                       depth=d,
#                                       k = rep(0:10, each=11),
#                                       ksay = rep(0:10, 11),
#                                       val=as.vector(sim.L)))
#       }
#     }
#   }
# }
# 
# write.csv(iteratedToM_liar, "lie-models/recursiveToM_sender_all.csv")
iteratedToM_liar <- read.csv("lie-models/recursiveToM_sender_all.csv")

iteratedToM_liar_weighted <- iteratedToM_liar %>%
  group_by(p, expt, mor, k, ksay) %>%
  mutate(w = dgeom(depth, 0.1) / sum(dgeom(0:40, 0.1))) %>% #normalize
  summarise(wval = sum(w*val)) %>%
  ungroup()
  
logliks_m <- data.frame(mor = numeric(), loglik = numeric())
for(m in unique(iteratedToM_liar$mor)){
  iteratedToM_liar_mX <- filter(iteratedToM_liar_weighted, mor==m)
  tempProd <- 0
  for(e in c("expt4","expt5")){
    for(prob in c(0.2, 0.5, 0.8)){
      for(t in 0:10){
        this.matr <- matrix(filter(iteratedToM_liar_mX,expt==e, p==prob)$wval, nrow=11, ncol=11) #matrix for p=0.2, 0.5, 0.8 are the same
        this.counts <- filter(countsLie, expt==e, probabilityRed==prob, drawnRed==t)
        n <- this.counts$n
        total <- sum(this.counts$n)
        loglik <- sum(log(this.matr[,(t+1)])*n) #equiv to log of product
        #log((factorial(total)/prod(factorial(n))) * prod(this.matr[,(t+1)]^n)) #delete later
        #loglik <- dmultinom(n, total, this.matr[,(t+1)], log=T)
        #print(paste(e, ",", "true =", t, ":", loglik))
        tempProd <- tempProd + loglik
      }
    }
  }
  logliks_m <- bind_rows(logliks_m, data.frame(mor=m, loglik=tempProd))
}

best.recursiveToM <- logliks_m %>%
  filter(loglik == max(loglik))

iteratedToM_liar_weighted %>%
  filter(mor == best.recursiveToM$mor) %>%
  mutate(expt = ifelse(expt == "expt4", "sender gets points for red", "sender gets points for blue"),
         expt = fct_relevel(expt,"sender gets points for red", "sender gets points for blue")) %>%
  ggplot(aes(x=k, y=ksay, fill=wval)) +
  geom_tile(stat="identity") +
  ggtitle(paste0("Recursive ToM + Aversion (η=",best.recursiveToM$mor,")")) +
  scale_x_continuous("true drawn k", breaks=seq(0,10,2), expand=c(0,0)) +
  scale_y_continuous("reported k*", breaks=seq(0,10,2), expand=c(0,0)) +
  scale_fill_gradient("predicted", low="white",high="navy") +
  facet_grid(expt ~ p)
ggsave("img/simpleModels/recursiveToM_sender.png", width=7, height=4.6)







recursiveToM_liar.pred.full <- iteratedToM_liar_weighted %>%
  filter(mor == best.recursiveToM$mor) %>%
  mutate(expt = ifelse(expt == "expt4", "sender gets points for red", "sender gets points for blue"),
         expt = fct_relevel(expt,"sender gets points for red", "sender gets points for blue"),
         p = as.factor(paste("p =",p)))

recursiveToM_liar.pred.red.fig <- recursiveToM_liar.pred.full %>%
  filter(expt == "sender gets points for red") %>%
  ggplot(aes(x=k, y=ksay, fill=wval)) +
  geom_tile() +
  scale_x_continuous("", breaks=seq(0,10,2), expand=c(0,0)) +
  scale_y_continuous("\n\nRecursive ToM", breaks=seq(0,10,2), expand=c(0,0)) +
  scale_fill_gradient(low="white",high="navy", limits=c(0,1)) +
  guides(fill=FALSE) +
  facet_wrap(~p) +
  theme_bw()

recursiveToM_liar.pred.blue.fig <- recursiveToM_liar.pred.full %>%
  filter(expt == "sender gets points for blue") %>%
  ggplot(aes(x=k, y=ksay, fill=wval)) +
  geom_tile() +
  scale_x_continuous("", breaks=seq(0,10,2), expand=c(0,0)) +
  scale_y_continuous("\n\nRecursive ToM", breaks=seq(0,10,2), expand=c(0,0)) +
  scale_fill_gradient(low="white",high="navy", limits=c(0,1)) +
  guides(fill=FALSE) +
  facet_wrap(~p) +
  theme_bw()

```

```{r}
countsLie.full <- countsLie %>%
  mutate(expt = ifelse(expt == "expt4", "sender gets points for red", "sender gets points for blue"),
         expt = fct_relevel(expt,"sender gets points for red", "sender gets points for blue"),
         probabilityRed = as.factor(paste("p =",probabilityRed))) %>%
  group_by(expt, probabilityRed, drawnRed) %>%
  mutate(condPropReport = n / sum(n))

ggplot(countsLie.full, aes(x=drawnRed, y=reportedDrawn, fill=condPropReport)) +
  geom_tile(stat="identity") +
  ggtitle("Human Results") +
  scale_x_continuous("true drawn k", breaks=seq(0,10,2), expand=c(0,0)) +
  scale_y_continuous("reported k*", breaks=seq(0,10,2), expand=c(0,0)) +
  scale_fill_gradient("proportion", low="white",high="navy") +
  facet_grid(expt ~ probabilityRed)
ggsave("img/simpleModels/humanResults_sender.png", width=7, height=4.6)




humanResults.pred.red.fig <- countsLie.full %>%
  filter(expt == "sender gets points for red") %>%
  ggplot(aes(x=drawnRed, y=reportedDrawn, fill=condPropReport)) +
  geom_tile() +
  scale_x_continuous("true drawn k", breaks=seq(0,10,2), expand=c(0,0)) +
  scale_y_continuous("\n\nHuman Results", breaks=seq(0,10,2), expand=c(0,0)) +
  scale_fill_gradient(low="white",high="navy", limits=c(0,1)) +
  guides(fill=FALSE) +
  facet_wrap(~probabilityRed) +
  theme_bw()

humanResults.pred.blue.fig <- countsLie.full %>%
  filter(expt == "sender gets points for blue") %>%
  ggplot(aes(x=drawnRed, y=reportedDrawn, fill=condPropReport)) +
  geom_tile() +
  scale_x_continuous("true drawn k", breaks=seq(0,10,2), expand=c(0,0)) +
  scale_y_continuous("\n\nHuman Results", breaks=seq(0,10,2), expand=c(0,0)) +
  scale_fill_gradient("proportion\nk* given k", low="white",high="navy", limits=c(0,1)) +
  #guides(fill=FALSE) +
  facet_wrap(~probabilityRed) +
  theme_bw()

sender_legend <- get_legend(humanResults.pred.blue.fig)
```


```{r}
liePred.red <- plot_grid(
  allLies.pred.red.fig, 
  someLies.pred.red.fig, 
  noToM_liar.pred.red.fig, 
  recursiveToM_liar.pred.red.fig, 
  humanResults.pred.red.fig, 
  nrow=5)
liePred.red.legend <- ggdraw() +
  draw_plot(
    plot_grid(
      liePred.red, 
      ggdraw() + draw_label("", fontface="bold", size=12, y=0.87, x=0.5, hjust=0, angle=270), 
      nrow=1, rel_widths=c(90, 10))) +
  draw_plot(sender_legend, x=0.45, y=0.025)
ggsave("img/simpleModels/allRed_sender.png", liePred.red.legend, width=7, height=10)


liePred.blue <- plot_grid(
  allLies.pred.blue.fig,
  someLies.pred.blue.fig,
  noToM_liar.pred.blue.fig,
  recursiveToM_liar.pred.blue.fig,
  humanResults.pred.blue.fig + theme(legend.position="none"), 
  nrow=5)
liePred.blue.legend <- ggdraw() +
  draw_plot(
    plot_grid(
      liePred.blue, 
      ggdraw() + draw_label("", fontface="bold", size=12, y=0.87, x=0.5, hjust=0, angle=270), 
      nrow=1, rel_widths=c(90, 10))) +
  draw_plot(sender_legend, x=0.45, y=0.025)
ggsave("img/simpleModels/allBlue_sender.png", liePred.blue.legend, width=7, height=10)
```



###fit MLE on depth

```{r}
# countsLie2 <- countsLie %>%
#   mutate(p = probabilityRed,
#          k = drawnRed,
#          ksay = reportedDrawn) %>%
#   select(expt, p, k, ksay, n) %>%
#   group_by(expt, p, k) %>%
#   mutate(sum = sum(n))
# 
# iteratedToM_liar_mor0 <- filter(iteratedToM_liar, mor==0)
# 
# depth.geometric <- function(d, val, depth){
#   d = logitToProb(pmin(9999, pmax(-9999, d)))
#   dgeom(depth, d)*val
# }
# 
# newVal = iteratedToM_liar_mor0$val*dgeom(iteratedToM_liar_mor0$depth, 0.1)
# mean.predicted <- function(){
#   
# }
# aggregate(newVal, by=list(ksay=iteratedToM_liar_mor0$ksay, 
#                           k=iteratedToM_liar_mor0$k, 
#                           p=iteratedToM_liar_mor0$p, 
#                           expt=iteratedToM_liar_mor0$expt), 
#           FUN=sum)
# depth.geometric.loglik <- function(y, d, k, ksay){
#   
#   sum(
#     pmax(dmultinom(y, 1, logistic.detect(kstar, beta, offset), log=T), -9999)
#   )
# }
# 
# depth.LL <- function(d){
#   expt = iteratedToM_liar_mor0$expt
#   p = iteratedToM_liar_mor0$p
#   depth = iteratedToM_liar_mor0$depth
#   k = iteratedToM_liar_mor0$k
#   ksay = iteratedToM_liar_mor0$ksay
#   val = iteratedToM_liar_mor0$val
#   actual = countsLie$n  
#   #d=probToLogit(0.1)
#   
#   weighted = aggregate(depth.geometric(d, val, depth), 
#                        by=list(ksay=ksay, 
#                                k=k, 
#                                p=p, 
#                                expt=expt), 
#                        FUN=sum)
#   countsLie3 <- countsLie2 %>%
#     left_join(weighted) %>%
#     group_by(expt, p, k) %>%
#     mutate(norm_x = x/sum(x))
#   
#   pred = 0
#   for(e in unique(countsLie3$expt)){
#     for(p in unique(countsLie3$p)){
#       for(k in unique(countsLie3$k)){
#         thisCount = countsLie3 %>%
#           filter(expt == e, p == p, k == k)
#         pred = pred + dmultinom(thisCount$n, thisCount$sum[1], thisCount$norm_x, log=T)
#       }
#     }
#   }
#   
#   #pred = depth.geometric(d, predicted, k, ksay)
#   neg.log.lik = -1*sum(pred)
#   neg.log.lik
# }

# depth.fit <- summary(mle(depth.LL,
#            start=list(d=rnorm(1,0,1)),
#            method = "BFGS"))
# iteratedToM_liar
```








## receiver / detector

### aware of utilities, unaware of baserate

$$P(BS \mid k^*) = f(k^* \mid \theta, SIGN(u))$$


$$\f() = logistic(k^*, \beta, \mu)$$
mu = sign(u)*offset + 5.5
beta = B*sign(u)

```{r}
logistic.detect <- function(kstar, beta, offset){
  y = beta*(kstar - offset)
  logitToProb(y)
}

logistic.loglik <- function(y, kstar, beta, offset){
  sum(
    pmax(dbinom(y, 1, logistic.detect(kstar, beta, offset), log=T), -9999)
  )
}

logistic.LL <- function(beta, offset){
  kstar = humanDetect$reportedDrawn
  y = as.logical(humanDetect$callBS)
  beta = ifelse(humanDetect$expt=="expt4", beta, -beta)
  
  neg.log.lik = -logistic.loglik(y, kstar, beta, offset)
  neg.log.lik
}

logistic.fit <- summary(mle(logistic.LL,
           start=list(beta=rnorm(1,0,0.5),
                      offset=rnorm(1,0,0.1)),
           method = "BFGS"))
logistic.fit
plot(0:10, logistic.detect(0:10, logistic.fit@coef['beta','Estimate'], logistic.fit@coef['offset','Estimate']))
```

### unaware of utilities, aware of baserate

$$P(BS \mid k^*) = \begin{cases}
k^* < E[k] & \Phi(k^* \mid k, p) \\
k^* > E[k] & 1-\Phi(k^* \mid k, p) \\
\end{cases}$$

```{r}
signifTesting.detect <- function(kstar, p){
  #binom.test(kstar, 10, p, alternative="two.sided")$p.value
  n = 10
  p = logitToProb(pmin(10, pmax(-10, p)))
  1-ifelse(kstar < n*p, pbinom(kstar, n, p, lower.tail=T), pbinom(kstar-1, n, p, lower.tail=F))
}

signifTesting.loglik <- function(y, kstar, p){
  sum(
    pmax(dbinom(y, 1, signifTesting.detect(kstar, p), log=T), -9999)
  )
}

signifTesting.LL <- function(p0.2, p0.5, p0.8){
  kstar = humanDetect$reportedDrawn
  y = as.logical(humanDetect$callBS)
  prob = humanDetect$probabilityRed
  p = case_when(
    prob == 0.2 ~ p0.2,
    prob == 0.5 ~ p0.5,
    prob == 0.8 ~ p0.8
   )
  
  neg.log.lik = -signifTesting.loglik(y, kstar, p)
  neg.log.lik
}

signifTesting.fit <- summary(mle(signifTesting.LL,
           start=list(p0.2=rnorm(1,0,2),
                      p0.5=rnorm(1,0,2),
                      p0.8=rnorm(1,0,2)),
           method = "BFGS"))
signifTesting.fit

data.frame(kstar=rep(0:10, 11*3), 
           p=rep(c(0.2,0.5,0.8), each=11),
           p.star = rep(c(signifTesting.fit@coef['p0.2','Estimate'], 
                          signifTesting.fit@coef['p0.5','Estimate'], 
                          signifTesting.fit@coef['p0.8','Estimate']), each=11)) %>%
  mutate(predicted = signifTesting.detect(kstar, p.star)) %>%
  ggplot(aes(x=kstar, y=predicted, colour=as.factor(p))) +
  geom_line()
humanLie.predSomeLies$predicted <- logitToProb(someLies.poisson(rep(rep(0:10, each=11),2), rep(0:10, 11*2), someLies.fit@coef['p','Estimate'], rep(c(1,-1),each=11*11), someLies.fit@coef['theta','Estimate'], someLies.fit@coef['weight','Estimate']))

```



### no ToM + aversion penalty --- no difference of aversion penalty

```{r}
p_t.ksay.r_p.L <- function(p, p.L) {
  P.K <- matrix(rep(p.k(0:numMarbles, p), each=numMarbles+1), nrow=numMarbles+1)
  P.L_KSAY.K <- p.L
  LIE = 1-diag(numMarbles+1)
  rowSums(P.K*P.L_KSAY.K*LIE)/rowSums(P.K*P.L_KSAY.K)
}

# noToM_detector <- data.frame(role=factor(),
#                       p=numeric(), 
#                       expt=factor(),
#                       mor=numeric(),
#                       ks=numeric(), # ksay in Detector, k in Liar
#                       val=numeric()) # prop in Detector, expLie in Liar
# moral = 0
# for(m in -5:25){
#   moral_receiver = m #calibrate receiver utility
#   for(i in c(0.2, 0.5, 0.8)){
#     for(j in c(4,5)){
#       Expt = j
#       sim.D <- mapply(p.D_bs.ksay.r,0:10, i, lastlvl=TRUE, p_t.ksay.r_p.L(i, rep(1/11,11)))
#       
#       noToM_detector <- bind_rows(noToM_detector,
#                          data.frame(role="Detector", p=i, expt=paste0("expt",j),
#                                             mor=m,
#                                             ks = rep(0:10),
#                                             val=as.vector(t(sim.D))))
#     }
#   }
# }
# write.csv(noToM_detector, "lie-models/noToM_receiver_all.csv")
noToM_detector <- read_csv("lie-models/noToM_receiver_all.csv")

full.counts.detect <- countsDetect %>%
  group_by(expt, reportedDrawn, callBS) %>%
  summarise(n = sum(n))

full.counts.detect.p <- countsDetect %>%
  group_by(expt, probabilityRed, reportedDrawn) %>%
  mutate(prop = n / sum(n)) %>%
  filter(callBS == "True") %>%
  select(-c(callBS, n))

logliks_randomOpp_m.d <- data.frame(mor = numeric(), loglik = numeric())
for(m in unique(noToM_detector$mor)){
  tempProd <- 0
  noToM_detector.mX <- filter(noToM_detector, mor==m)
  for(e in c("expt4","expt5")){
    for(prob in c(0.2, 0.5, 0.8)){
      # tempProd <- 0
      for(t in 0:10){
        this.prob <- filter(noToM_detector.mX,expt==e, p==prob, ks==t)$val #vector for p=0.2, 0.5, 0.8 are the same
        this.counts <- filter(countsDetect, expt==e, probabilityRed==prob, reportedDrawn==t)
        n <- filter(this.counts, callBS=="True")$n
        total <- sum(this.counts$n)
        loglik <- log(this.prob)*n + log(1-this.prob)*(total-n)
        # loglik <- dbinom(n, total, this.prob, log=T)
        #print(paste(e, ", p =", prob, "true =", t, ":", loglik))
        tempProd <- tempProd + loglik
      }
    }
  }
  logliks_randomOpp_m.d <- bind_rows(logliks_randomOpp_m.d, data.frame(mor=m, loglik=tempProd))
}
logliks_randomOpp_m.d

best.randOpp.receiver <- logliks_randomOpp_m.d %>%
  filter(-loglik == min(-loglik))

# using at BS calling aversion by condition
noToM_detector %>%
  filter(mor == best.randOpp.receiver$mor) %>%
  ggplot(aes(x=ks, y=val, colour=as.factor(p), linetype=expt)) +
  geom_point(alpha=0.8) +
  geom_line() +
  theme_minimal()
```


#### iterated recursive detector behavior

```{r}
# iteratedToM_detector <- data.frame(role=factor(),
#                       p=numeric(),
#                       expt=factor(),
#                       mor=numeric(),
#                       depth=numeric(),
#                       ks=numeric(), # ksay in Detector
#                       val=numeric()) # prop in Detector
# 
# for(i in c(0.2, 0.5, 0.8)){
#   for(j in c(-5:25)){
#     moral_receiver = j
#     for(k in c(4,5)){
#       Expt = k
#       for(d in 0:40){
#         sim.D <- mapply(p.D_bs.ksay.r,0:10, i, lastlvl=TRUE, iterate.L(d,i, rep(0.5,11)))
# 
#         iteratedToM_detector <- bind_rows(iteratedToM_detector,
#                                 data.frame(role="Detector", p=i, expt=paste0("expt",k),
#                                       mor=j,
#                                       depth=d,
#                                       ks = 0:10,
#                                       val=as.vector(t(sim.D))))
#       }
#     }
#   }
# }
# write.csv(iteratedToM_detector, "lie-models/recursiveToM_receiver_all.csv")
iteratedToM_detector <- read.csv("lie-models/recursiveToM_receiver_all.csv")


iteratedToM_detector_weighted <- iteratedToM_detector %>%
  group_by(p, expt, mor, ks) %>%
  mutate(w = dgeom(depth, 0.1) / sum(dgeom(0:40, 0.1))) %>%
  summarise(wval = sum(w*val))


logliks_m.d <- data.frame(mor = numeric(), loglik = numeric())
for(m in unique(iteratedToM_detector$mor)){
  iteratedToM_detector_mX <- filter(iteratedToM_detector_weighted, mor==m)
  tempProd <- 0
  for(e in c("expt4","expt5")){
    for(prob in c(0.2, 0.5, 0.8)){
      for(t in 0:10){
        this.prob <- filter(iteratedToM_detector_mX,expt==e, p==prob, ks==t)$wval #matrix for p=0.2, 0.5, 0.8 are the same
        this.counts <- filter(countsDetect, expt==e, probabilityRed==prob, reportedDrawn==t)
        n <- filter(this.counts, callBS=="True")$n
        total <- sum(this.counts$n)
        loglik <- log(this.prob)*n + log(1-this.prob)*(total-n)
        # loglik <- dbinom(n, total, this.prob, log=T)
        #print(paste(e, ",", "p =", prob, "true =", t, ":", loglik))
        tempProd <- tempProd + loglik
      }
    }
  }
  logliks_m.d <- bind_rows(logliks_m.d, data.frame(mor=m, loglik=tempProd))
}

best.recursiveToM.receiver <- logliks_m.d %>%
  filter(loglik == max(loglik))
```



```{r}
senderModels = c(
  "EverybodyLies", 
  "SomePeopleLie", 
  "RandomOpponent", 
  "RecursiveToM"
)
senderValues = c(
  "EverybodyLies" = bquote(atop("Everybody Lies","Heuristic")), 
  "SomePeopleLie" = bquote(atop("Some People Lie","Heuristic")), 
  "RandomOpponent" = bquote("Random Opponent ("*eta*"="*.(best.randOpp$mor)*")"), 
  "RecursiveToM" = bquote("Recursive ToM ("*eta*"="*.(best.recursiveToM$mor)*")")
)
senderLikelihood = c(
  allLies.fit@m2logL/2, 
  someLies.fit@m2logL/2, 
  -best.randOpp$loglik, 
  -best.recursiveToM$loglik
)

senderAIC = c(
  allLies.fit@m2logL + 2*2, 
  someLies.fit@m2logL + 2*3, 
  -2*best.randOpp$loglik + 2*2, 
  -2*best.recursiveToM$loglik + 2*3
)

receiverModels = c(
  "NHST", 
  "RandomOpponent", 
  "RecursiveToM"
)
receiverValues = c(
  "NHST" = bquote(atop("Null Hypothesis","Significance Testing")), 
  "RandomOpponent" = bquote("Random Opponent ("*eta*"="*.(best.randOpp.receiver$mor)*")"), 
  "RecursiveToM" = bquote("Recursive ToM ("*eta*"="*.(best.recursiveToM.receiver$mor)*")")
)
receiverLikelihood = c(
  signifTesting.fit@m2logL/2, 
  -best.randOpp.receiver$loglik, 
  -best.recursiveToM.receiver$loglik
)

receiverAIC = c(
  signifTesting.fit@m2logL + 2*3, 
  -2*best.randOpp.receiver$loglik + 2*2, 
  -2*best.recursiveToM.receiver$loglik +2*3
)


axisLineSize = 1
axisLineColour = "black"
axisTitleSizeComp = 12
axisTextSizeComp = 8

senderModelFig <- data.frame(model = senderModels,
           loglik = senderAIC) %>%
  mutate(model = fct_relevel(model,
                         "EverybodyLies",
                         "SomePeopleLie",
                         "RandomOpponent",
                         "RecursiveToM")) %>%
  ggplot(aes(x=model, y=loglik)) +
  geom_bar(stat="identity", fill="gray40", colour="black") +
  scale_x_discrete("", labels=senderValues) +
  scale_y_continuous("Sender reporting k* given true k\nAIC", limits=c(0, 30000), expand=c(0,0)) +
  theme_minimal() +
  theme(axis.title = element_text(size=axisTitleSizeComp),
        axis.text = element_text(size=axisTextSizeComp),
        axis.line = element_line(size=axisLineSize, colour=axisLineColour))

receiverModelFig <- data.frame(model = receiverModels,
           loglik = receiverAIC) %>%
  mutate(model = fct_relevel(model,
                         "NHST",
                         "RandomOpponent",
                         "RecursiveToM")) %>%
  ggplot(aes(x=model, y=loglik)) +
  geom_bar(stat="identity", colour="black", fill="gray40") +
  scale_x_discrete("Model", labels = receiverValues) +
  scale_y_continuous("Receiver calling BS given reported k*\n-AIC", limits=c(0, 30000), expand=c(0,0)) +
  theme_minimal() +
  theme(axis.title = element_text(size=axisTitleSizeComp),
        axis.text = element_text(size=axisTextSizeComp),
        axis.line = element_line(size=axisLineSize, colour=axisLineColour))

plot_grid(senderModelFig, receiverModelFig, nrow=2)
ggsave("img/simpleModels/loglikelihoods.pdf", height=7, width=7)
```




### Compare Lying Aversion

```{r}
# ll.lie.df.prev <- logliks_m %>%
#   filter(mor >= 4 & mor <= 5) %>%
#   mutate(mor=mor+1,
#          ll.lie.prev = loglik) %>%
#   select(mor, ll.lie.prev)
# ll.lie.A <- logliks_m %>%
#   filter(mor >= 5 & mor <= 6) %>%
#   select(mor, loglik) %>%
#   left_join(ll.lie.df.prev) %>%
#   mutate(diff.bw = -loglik-(-ll.lie.prev)) %>%
#   summarise(diff = diff(diff.bw)) %>%
#   .$diff
# (se.lie.A = sqrt(1/ll.lie.A))
# 
# 
# ll.detect.df.prev <- logliks_m.d %>%
#   filter(mor >= 10 & mor <= 11) %>%
#   mutate(mor=mor+1,
#          ll.detect.prev = loglik) %>%
#   select(mor, ll.detect.prev)
# ll.detect.A <- logliks_m.d %>%
#   filter(mor >= 11 & mor <= 12) %>%
#   select(mor, loglik) %>%
#   left_join(ll.detect.df.prev) %>%
#   mutate(diff.bw = -loglik-(-ll.detect.prev)) %>%
#   summarise(diff = diff(diff.bw)) %>%
#   .$diff
# (se.detect.A = sqrt(1/ll.detect.A))
# 
# wald.z.test <- function(m1, sd1, m2, sd2){
#   z <- (m1 - m2) / sqrt(sd1^2 + sd2^2)
#   p <- pnorm(abs(z), lower.tail=F)
#   return(data.frame(m1, sd1, m2, sd2, z, p))
# }
# 
# wald.z.test(5, se.lie.A, 11, se.detect.A)
```





```{r}
logliks_m %>%
  mutate(source="sender") %>%
  bind_rows(mutate(logliks_m.d, source="receiver")) %>%
  group_by(source) %>%
  filter(loglik==max(loglik))
```



